---
title: "Data Analysis"
---

## Graphs

Initially lets upload the data.

```{r}
data <- read.csv(file = "/Users/user/Desktop/Final Project/vazgen.csv")

```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

And now lets call libraries, which will help us to create graphs

```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

And finally its time for graphs

Now we know what is PM, and now lets watch some graphs abt it depending on temperature\

```{r warning=FALSE}
data |>
  ggplot(mapping = aes(x = temperature, y = pm10, color = as.factor(direction)))+
  geom_point() +  
  facet_wrap(~direction , strip.position="bottom") +
  theme(legend.position="none")+
  scale_y_log10()+
  labs(title = "Number of PM10 in the air depending on Temperature",
    x  = "Temperature(째C)",
       y = "PM10")
```

```{r warning=FALSE}
library(plotly)
p <- data |>
 filter(direction == "N" | direction == "S" |direction == "E"|direction == "W")|>
  ggplot(mapping = aes(x = temperature, y = pm10,size = pm10, color = as.factor(direction))) +
  geom_point(alpha = 0.3, show.legend = FALSE)+
  scale_size(range = c(2, 12)) +
  facet_wrap(~direction)+
  theme(legend.position="none")+
  geom_smooth(color = "#e9ecef")+
  labs(
    title = "Quantity of PM10 in the air",
    x = "Temperature(째C)",
    y = "PM10"
  ) 
ggplotly(p)
```

```{r warning=FALSE}
m <- data |>
 filter(direction == "NE" | direction == "SE" |direction == "SW"|direction == "NW")|>
  ggplot(mapping = aes(x = temperature, y = pm10,size = pm10, color = as.factor(direction))) +
  geom_point(alpha = 0.2, show.legend = FALSE)+
  scale_size(range = c(2, 12)) +
  facet_wrap(~direction) +
  theme(legend.position="none")+
  geom_smooth(color = "#e9ecef")+
  labs(
    title = "Quantity of PM10 in the air",
    x = "Temperature(째C)",
    y = "PM10"
  ) 
ggplotly(m)
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

The 4th graph is abt the temperature during the year

```{r warning=FALSE}

hist <- data |>
  
  select(temperature, pressure)|>
  ggplot(mapping = aes(x = temperature, fill = temperature))+
  geom_histogram(binwidth = 0.3,color = "white", fill = "#1b9aaa")+

scale_x_continuous(breaks = seq(-20, 50, by = 2))+
scale_y_continuous(breaks = seq(0, 500, by = 20))+
  labs(title = "Temperature in Armenia",
       x = "Temperature(째C)",
       y = "Count"
       )
ggplotly(hist)
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

This graph is like the previous one, but this one is abt the pressure

```{r warning=FALSE}
hist2 <- data |>
  ggplot(mapping = aes(x = pressure, fill = pressure))+
  geom_histogram(color = "#d9d9d9", fill = "#3c6e71", bins = 30)+
  theme_minimal()+
  theme_light()+
scale_x_continuous(breaks = seq(600, 900, by = 25))+
scale_y_continuous(breaks = seq(0, 10000, by = 1000))+ 
  labs(title = "Pressure in Armenia",
       x = "Pressure",
       y = "Count")
ggplotly(hist2)
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

This one is a density graph, which depends on direction

```{r}
data|>
  ggplot(mapping = aes(x = direction))+
  geom_density(aes(fill=factor(direction), alpha = 1))+
  scale_y_continuous(breaks = seq(0, 2, by = 0.1))+
  labs(title = "The Density of Directions",
       x = "Direction",
       y = "Density",
       alpha = "Alpha",
       fill = "Colors of Directions")
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

Here's another density graph depending on rain

```{r warning=FALSE}
data |>
  arrange(rain)|>
  select(time,rain)|>
  ggplot(mapping = aes(x = rain))+
  labs(x = "Rain",
       y = "Density",
       alpha = "Alpha",
       fill = "Rain(mm)")+
  ggtitle("The density of the rain")+
  geom_density(aes(fill=factor(rain), alpha = 1))+
  scale_x_continuous(breaks = seq(0, 5, by = 0.25))+
  scale_y_continuous(breaks = seq(0, 5, by = 1))
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

Here's a box plot abt the speed of directions

```{r}
data |>
  filter(speed > 0.1 ) |>
  group_by(direction)|>
  select(direction, speed)|>
  ggplot(mapping = aes(x = direction, y = speed))+
  geom_boxplot(alpha = 0.28, color = "#1b9aaa",fill = "#06d6a0")+
  labs(title = "Speed of Directions in November",
       x = "Direction",
       y = "Speed")+
scale_y_continuous(breaks = seq(0, 50, by = 1))
```

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

And the last one.

A correlogram of our data

```{r}
library(ggcorrplot)

database <- na.omit(data)
numeric_columns <- sapply(database, is.numeric)
corr <- round(cor(database[, numeric_columns]), 1)

ggcorrplot(corr, hc.order = TRUE, 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           method = "circle", 
            colors = c("#a873e8", "#ebc2ff", "#56d1dc"),
           title = "Correlogram of Our Dataset", 
           ggtheme = theme_bw)
```
